\begin{thebibliography}{99}

\bibitem{AS} {\sc Abramovich, F. y Steinberg, D.}, {\it Improved Inference in Nonparametric Regression using Lk Smoothing Splines}. Journal of Statistical Planning, 49: 327-341, 1996.

\bibitem{Mm} {\sc Maita B. Miriam A.}, {\it Estimaci\'on de una curva de rendimientos para los bonos de la deuda p\'ublica interna en Venezuela}, (trabajo de grado Maestr\'ia en Administraci\'on de Empresas menci\'on Finanzas).  Universidad Cat\'olica Andr\'es Bello, Caracas, Venezuela, 2010.

\bibitem{NS} {\sc Nelson, C. y Siegel, A.} {\it Parsimonius Modeling of Yield Curves}. Journal of
Business, $60$: $473$-$489$, 1987.

\bibitem{DO} {\sc Douglas, L.G.} {\it Yield Curve Analysis}. New York Institute of Finance, 1988.


\bibitem{Sv} {\sc Svensson, L.} {\it Estimating and Interpreting Forward Interest Rates: Sweden 1992-1994}, NBER Working Papers, 4871. Estocolmo: National Bureau of Economic Research, 1994.

\bibitem{HT} {\sc Hunt, B. y Terry, C.} {\it Zero-Coupon Yield Curve Estimation: A Principal Component-Polynomial Approach}, Technical report 81. Sydney: University of Technology Sydney - School of Finance and Economics, 1998.

\bibitem{H} {\sc Hunt, B.} {\it Modelling the Yields on Australian Coupon Paying Bonds}, Technical report 9. Sydney: University of Technology Sydney - School of Finance and Economics, 1995.

\bibitem{Ha} {\sc Haykin, S.} {\it Neural Networks}. New York: McMillan College Publishing Company, 1994.

\bibitem{IG} {\sc Isasi, P. y Galv\'an, I.} {\it Redes neuronales artificiales: un enfoque pr\'actico.}. Madrid: Pearson-Prentice Hall, 2004.

\bibitem{KB} {\sc Kaastra, I. y Boyd, M.} {\it Design a Neural Network for Forecasting Financial and Economic Time Series}. Neurocomputing 10: 215-236, 1996.

\bibitem{NW} {\sc Nocedal, J. y Wright, S.} {\it Numerical Optimization}. New York: Springer-Verlag, 1999.


\bibitem{FG} {\sc Fan, J. y Gijbels, I.} {\it Local Polynomial Modelling and Its Applications}. New York: Chapman and Hall, 1996.

\bibitem{BW} {\sc B.W. Silverman.} {\it Some Aspects of the Spline Smoothing Approach to Non-Parametric Regression Curve Fitting}. Journal of the Royal Statistical Society. Series B (Methodological), Vol. 47, No. 1, 1(1985), pp. 1-52, 1984.


\bibitem{F} {\sc Friedman, J. H.} {\it A Variable Span Smoother}, Technical report 5. Standford:
Standford University - Departament of Statistics, 1984.


\bibitem{SH} {\sc Sharda, R.} {\it Neural networks for the MS/OR analyst: An application bibliography}. Interfaces, 24(2): 116-130, 1994.

\bibitem{SVM} {\sc Suykens, J.; Vandewalle, J. y Moor, B. D.} {\it Artificial Neural Networks for Modelling and Control of Nonlinear Systems.}. Boston: Kluwer Academic Publishers, 1996.

\bibitem{FR} {\sc Fern\'andez J.L., Robles, M.D.}  {\it Teor\'ia de las Expectativas y Cambio Estructural: nueva evidencia en los tipos a corto plazo espa\~noles.} Tribuna de Econom\'ia No. 827. ICE, 2005.

\bibitem{YS} {\sc Yung-Shi Liau, Jack J.W. Yang.} {\it The Expectations Hypothesis of Term Structure of Interest Rates in Taiwan's Money Market.} International Research Journal of Finance and Economics, 2009.

\bibitem{ZPH} {\sc Zhang, G.; Patuwo, B. y Hu, Y.} {\it Forecasting with Artificial Neural Networks: The State of Art.} International Journal of Forecasting, 14: 35-62, 1998.

\end{thebibliography}
